### 2016-11-09 datamining/summery.tex
Added a large portion of frequent pattern mining

@@

>>>>

You have the reverse opperation because hillclimbing only looks one step ahead,
therefore adding and deleting can't emulate it.

@@

\section{Frequent pattern mining}
$\Sigma$ is the set of labels, $s=s_1,_2,\dots,s_n$ where $s_i \in \Sigma$,
prefix $s[1:i]=s_1,s_2,\dots,s_1, 0 \leq i \leq n$. suffix $s[i:n]$.
Let $s=s_1,s_2\dots s_n$ and $r=r_1,r_2,\dots r_m$ be two sequences over
$\Sigma$. We say $r$ is a subsequence of $s$ denoted $r \subseteq s$, if there
exists a one-to-one mapping $\phi:[1,m]\to[1,n]$ such that $r[i]=s[\phi(i)]$ and
$i< j \Rightarrow \phi(i)<\phi(j)$.
Each position in $r$ is mapped to a position in $s$ with the same label and the
orer of labels is preserved. There may however be interverning gapsbetween
consecutive elements of $r$ in the mapping.
Given a database $D={s_1,\dots,s_N}$ of $N$ sequences and given some sequenc $r$
the suport is defined as the total number of seuences in $D$ that contain $r$:
$sup(r)=|\{s_i\in D:r\subseteq s_i\}|$. Given a minimum support threshold minsup,
compute $\mathcal{F}(minsup,D)=\{r|sup(r)\leq minsup\}$.
For two sequences $r_1$ and $r_2$ we have $r_1 \subseteq r_2 \Rightarrow
sup(r_1) \leq sup(r_2)$ becuase $\forall s \in D: r_2 \subseteq s \Rightarrow
r_1 \subseteq s$
Hence in a level wise search for frequent sequences there is no point in
expending infrequent ones.
\subsection{GSP algorthm}
Perform level wise search. Don't extend infrequent sequences.
Candiadate generation for level $k+1$: take two frequent sequences $r_a$ and
$r_b$ of length $k$ with $r_a[q:k-1]=r_b[1:k-1]$ and generate pre-candadate
$r_{ab}=r_a+r_b[k]$. Pre-candidate $r_{ab}$ becomes a candidate (has to be
counted) if all its subsequences of length $k$ are frequent. Note that we allow
$r_a = r_b$.
\subsection{Node labeled Graph}
